### 2017-02-21 thesis/results/results2.tex
tmp commit

\begin{table}[htpb]
	\centering
	\caption{Description of the linear models used to predict the CR obesity metagene, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
	\label{tab:lm_pr_only}
	\begin{threeparttable}
			\begin{tabular}{llrS[detect-weight]}
				Linear Model & Variables & Estimate &P-value\\
				\hline
				\hline
				\rule{0pt}{2.25ex}\gls{pr}-only & \gls{pr}   & 0.477  & {\num{6.06d-7}}\tnote{1}\\
			\end{tabular}
			\begin{tablenotes}
				\item [1] All values in bold are statistically significant (p \textless{} 0.05).
			\end{tablenotes}
	\end{threeparttable}
\end{table}
% \begin{table}[htpb]
% 	\centering
% 	\caption{Description of the linear models used to predict the CR obesity metagene, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
% 	\label{tab:lm_pr_only}
% 	\begin{threeparttable}
% 			\begin{tabular}{llrS}
% 				Linear Model & Variables & Estimate &P-value\\
% 				\hline
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{pr}-only                            & \gls{pr}   & 0.477  & \num{6.06d-7}\tnote{1}\\
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002 & 0.586\\
%                                                                            & \gls{pr}   & 0.478  & 6.35 \times10^{-7}\\
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.085 & 0.176\\
%                                                                            & Overweight & -0.011 & 0.875\\
%                                                                            & \gls{pr}   & 0.471  & 8.25 \times10^{-7}\\
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007  & 0.237\\
%                                                                            & Obese      & -0.188 & 0.081\\
%                                                                            & Overweight & -0.049 & 0.516\\
%                                                                            & \gls{pr}   & 0.459  & 1.54 \times10^{-6}\\
% 				\hline
% 				\hline
% 			\end{tabular}
% 			\begin{tablenotes}
% 				\item [1] All values in bold are statistically significant (p \textless{} 0.05).
% 			\end{tablenotes}
% 	\end{threeparttable}
% \end{table}

>>>>

\bfseries \num{6.06d-7}

\begin{table}[htpb]
	\centering
	\caption{Description of the linear models used to predict the CR obesity metagene, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
	\label{tab:lm_pr_only}
	\begin{threeparttable}
			\begin{tabular}{llrS}
				Linear Model & Variables & Estimate & {P-value}\\
				\hline
				\hline
				\rule{0pt}{2.25ex}\gls{pr}-only                            & \gls{pr}   & 0.477  & {\bfseries \num{6.06d-7}}\tnote{*}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002 & 0.586\\
                                                                           & \gls{pr}   & 0.478  & {\bfseries \num{6.35d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.085 & 0.176\\
                                                                           & Overweight & -0.011 & 0.875\\
                                                                           & \gls{pr}   & 0.471  & {\bfseries \num{8.25d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007  & 0.237\\
                                                                           & Obese      & -0.188 & {\bfseries 0.081}\\
                                                                           & Overweight & -0.049 & 0.516\\
                                                                           & \gls{pr}   & 0.459  & {\bfseries \num{1.54d-6}}\\
				\hline
				\hline
			\end{tabular}
			\begin{tablenotes}
				\item [*] All values in bold are statistically significant (p \textless{} 0.05).
			\end{tablenotes}
	\end{threeparttable}
\end{table}
% \begin{table}[htpb]
% 	\centering
% 	\caption{Description of the linear models used to predict the CR obesity metagene, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
% 	\label{tab:lm_pr_only}
% 	\begin{threeparttable}
% 			\begin{tabular}{llrS}
% 				Linear Model & Variables & Estimate &P-value\\
% 				\hline
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{pr}-only                            & \gls{pr}   & 0.477  & \num{6.06d-7}\tnote{1}\\
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002 & 0.586\\
%                                                                            & \gls{pr}   & 0.478  & 6.35 \times10^{-7}\\
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.085 & 0.176\\
%                                                                            & Overweight & -0.011 & 0.875\\
%                                                                            & \gls{pr}   & 0.471  & 8.25 \times10^{-7}\\
% 				\hline
% 				\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007  & 0.237\\
%                                                                            & Obese      & -0.188 & 0.081\\
%                                                                            & Overweight & -0.049 & 0.516\\
%                                                                            & \gls{pr}   & 0.459  & 1.54 \times10^{-6}\\
% 				\hline
% 				\hline
% 			\end{tabular}
% 			\begin{tablenotes}
% 				\item [1] All values in bold are statistically significant (p \textless{} 0.05).
% 			\end{tablenotes}
% 	\end{threeparttable}
% \end{table}
